An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-09-17 neurips-19/poly-embed.tex
Changed some proposed additions

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessie Finocchiaro\raf{Jessie?} \\
 \texttt{jefi8453@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo\\
 \texttt{bwag@colorado.edu}\\
 MSFT
}

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.

@@

Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

@@

Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper,\footnote{Citation withheld for anonymity.\raf{And because it's not up yet!}} and focus here on the $k=2$ case.
For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
\begin{multline}
  \label{eq:lovasz-hinge}
  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
\end{multline}
where $(x)_+ = \max\{x,0\}$.
We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.

@@

In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
In the full version of the paper\raft{add cite later}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.

@@

\begin{figure}
	\begin{minipage}{0.4\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/original-top-k}
		\label{fig:original-top-k}
	\end{minipage}
	\hfill
	\begin{minipage}{0.4\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
		\label{fig:finite-surrogate-top-k}
	\end{minipage}
	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$. 
%\raf{The projection is off somehow; uniform distribution should be the centroid, and more generally, both figures should be rotationally symmetric.}
	}
	\label{fig:top-k-simplices}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
%We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
%While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
%Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.

@@

\raf{ACKNOWLEDGEMENTS (commented out for submission)}
\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several important insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}.
This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

@@

\raft{Note for later: should be able to show that the union of trim is the simplex.}
Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.

@@

\hrule
\bigskip
TODO for camera-ready (tagging the person who'll probably end up doing it)
\begin{enumerate}
	\item \jessie{Make poster and link to it online}
	\item All: Address todos in paper.
	\item OPTIONAL: Make/link to slides and/or on paper
	\item Reviewer 1
	\begin{enumerate}
		\item \jessie{Clarify terms like \emph{reports} and \emph{properties}.}
	\end{enumerate}
	\item Reviewer 2 (didn't change review)
	\begin{enumerate}
		\item Provide more intuition for definitions
	\end{enumerate}
	\item Reviewer 3 (didn't change review)
	\begin{enumerate}
		\item \raf{Add discussion on the computational complexity (or lack thereof) of constructing $L$ and $\psi$}
		\item \jessie{Make sure we have corrected top-$k$ proof.}
	\end{enumerate}
	\item Meta-Review: ``Inserting all the comments made to answers R2 and R3 is a must for the paper to be very good.''
\end{enumerate}

>>>>

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{[PROPOSED ADDITION: #1]}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessie Finocchiaro \\
 \texttt{jefi8453@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo Waggoner\\
 \texttt{bwag@colorado.edu}\\
 Microsoft Research, New York City
}

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.
\jessie{R2 asked for more intuition on this definition... not sure what more to add}

\proposedadd{We focus on polyhedral losses in this context because, as Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent} point out, smooth surrogates that estimate the conditional probability generally do much more than necessary, or practical in many cases.  In minimizing a polyhedral loss, they make the argument that one only learns what is necessary, in accordance with Vapnik's dictum~\cite[Section 1.9]{vapnik1999nature}.}

@@

\proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.  In this case, we can think of $p$ as the conditional probability $p = Pr[Y = y | X = x]$ when the true distribution is over $\X \times\Y$.  Throughout, we abstract away the input $X \sim \X$ and can work with these conditional probabilities $p \in \simplex$.}
Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, \proposedadd{; that is, $\Gamma(p)$ is the prediction that minimizes expected loss when the outcome $Y \sim p$.  Moreover, \ldots} and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

\proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computer once.  They are generally derived mathematically, rather than computationally.  These symbolically calculations typically tend to be straightforward, but can sometimes be tricky.}

@@

Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper~\cite{finocchiaro2019embedding}, and focus here on the $k=2$ case.
For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
\begin{multline}
  \label{eq:lovasz-hinge}
  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
\end{multline}
where $(x)_+ = \max\{x,0\}$.
We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.

@@

In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
In the full version of the paper~\cite{finocchiaro2019embedding}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.

@@

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/original-top-k}
		\label{fig:original-top-k}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{tikz/finite-surrogate-top-k}
		\label{fig:finite-surrogate-top-k}
	\end{minipage}
	\caption{Minimizers of $\inprod{p}{\elltop{2}}$ and $\inprod{p}{\ell^2}$, respectively, varying $p$ over $\Delta_3$.}
	\label{fig:top-k-simplices}
\end{figure}

\proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.  Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
\begin{align*}
\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
\end{align*}
The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
\begin{equation}
\ell^{top-k}(r,y) = \begin{cases}
0 & r_y = \bar r_{-y} + 1\\
\bar r - \frac 1 k & r_y = 1\\
1 + \bar r & r_y = 0
\end{cases}~,~
\end{equation}
where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
\proposedadd{We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.}

@@

\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several important insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

@@

\btw{RF: Note for later: should be able to show that the union of trim is the simplex.}
Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.

@@

\hrule
\bigskip
TODO for camera-ready (tagging the person who'll probably end up doing it)
\begin{enumerate}
	\item \jessie{Make poster and link to it online}
	\item All: Address todos in paper.
	\item OPTIONAL: Make/link to slides and/or on paper
	\item Reviewer 1 (Didn't change review)
	\begin{enumerate}
		\item Clarify terms like \emph{reports} and \emph{properties}. \jessie{Done}
	\end{enumerate}
	\item Reviewer 2 (didn't change review)
	\begin{enumerate}
		\item Motivate polyhedral losses
		\item Definitions 1-3 intuition \jessie{Done}
	\end{enumerate}
	\item Reviewer 3 (didn't change review)
	\begin{enumerate}
		\item Add discussion on the computational complexity (or lack thereof) of constructing $L$ and $\psi$.
		\item \jessie{Make sure we have corrected top-$k$ proof.}
	\end{enumerate}
	\item Meta-Review: ``Inserting all the comments made to answers R2 and R3 is a must for the paper to be very good.''
\end{enumerate}
